working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect

### 2018-12-07 Manuscript_draft/Manuscript_draft.Rmd
knitting to word

---
title: working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect
author:
- affilnum: '1,2,3'
  name: Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
  email: barragansljose@gmail.com
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
- affil: Big Name University, Department of R, City, BN, 01020, USA
  affilnum: 2
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 3
output:
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  word_document: null
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---

>>>>

---
title: working title Compatibility system and stygma size of pollen recipient as main predictors of heterospecific pollen effect
author:
- affilnum: '1,2,3'
  name: Jose B. Lanuza, Ignasi Bartomeus, Tia-Lynn Ashman, Romina Rader
  email: barragansljose@gmail.com
affiliation:
- affil: US Environmental Protection Agency, Office of Research and Development, National
    Health and Environmental Effects Research Laboratory, Atlantic Ecology Division,
    27 Tarzwell Drive  Narragansett, RI, 02882, USA
  affilnum: 1
- affil: Big Name University, Department of R, City, BN, 01020, USA
  affilnum: 2
- affil: Estacion Biologica de Donana (EBD-CSIC), E-41092 Sevilla, Spain
  affilnum: 3
output:
  word_document: null
  pdf_document:
    fig_caption: yes
    fig_height: 7
    fig_width: 7
    includes:
      in_header: header.tex
    keep_tex: yes
    number_sections: no
    template: manuscript.latex
  html_document: null
capsize: normalsize
classoption: a4paper
csl: ecology.csl
documentclass: article
fontsize: 11pt
footerdate: yes
geometry: margin=1in
linenumbers: yes
bibliography:
- references.bib
- knitcitations.bib
spacing: doublespacing
abstract: no
---
